Self-Supervised Learning of Generalized Policies in adversarial domains

### 2021-05-12 doc/paper/paper.tex
some changes in encogin and documentation

\subsection{Space Invaders - v0}
\subsubsection{Description}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
    (A) Num[col-hv-Agent] [k=1]
    (B) Dist[col-hv-white_king;right_col;col-hv-black_king] [k=4]
\end{Verbatim}

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. B=0 AND A>0 -> {B INCs, A DECs}, {B NILs, A NILs}, {B INCs, A NILs}
  2. B>0 AND A>0 -> {B DECs, A NILs}, {B NILs, A NILs}, {B INCs, A DECs}, {B NILs, A DECs}
\end{Verbatim}

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]

@@

\subsection{Chase}
\subsubsection{Description}
In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $rightup$, $right$, $rightdown$, $down$, $leftdown$, $left$, $leftup\}$. The agent can move only diagonally and the adversary can move in perpendicular directions.

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col_has_Agent,Exists(right_col,col_has_Target))] [k=5]
  (B) Bool[And(row_has_Target,Exists(up_row,row_has_Agent))] [k=5]
  (C) Dist[row_has_Target;up_row;row_has_Agent] [k=4]
  (D) Dist[col_has_Agent;right_col;col_has_Target] [k=4]
\end{Verbatim}

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND D>0 AND C>0 -> {A NILs, B NILs, C DECs, D DECs}, {A INCs, B INCs, C DECs, D DECs},
                                    {A INCs, B NILs, C DECs, D DECs}, {A NILs, B INCs, C DECs, D DECs}
  2. A>0 AND B=0 AND D>0 AND C>0 -> {A DECs, B INCs, C DECs, D DECs}, {A DECs, B NILs, C DECs, D DECs}
  3. A=0 AND B=0 AND D>0 AND C=0 -> {A NILs, B INCs, C INCs, D DECs}, {A INCs, B INCs, C INCs, D DECs}
  4. A=0 AND B=0 AND D=0 AND C>0 -> {A INCs, B INCs, C DECs, D INCs}, {A INCs, B NILs, C DECs, D INCs}
  5. A=0 AND B>0 AND D>0 AND C>0 -> {A NILs, B DECs, C DECs, D DECs}, {A INCs, B DECs, C DECs, D DECs}
\end{Verbatim}

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
....... # ....... # ....... # ....T.. # ...T... # ...T... #
....... # ....... # ....T.. # ....... # ....... # ...A... #
....... # ....T.. # ....... # ....... # ....A.. # ....... #
....T.. # ....... # ....... # ...A... # ....... # ....... #
....... # ....... # ..A.... # ....... # ....... # ....... #
....... # .A..... # ....... # ....... # ....... # ....... #
A...... # ....... # ....... # ....... # ....... # ....... #
\end{Verbatim}

\subsection{Shoot}
\subsubsection{Description}
In this domain an agent has to shoot an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$. This game would be the equivalent of a check with the rook. Only that both the rook and the opponent can only move one orthogonal square at a time.

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-has-Adversary,col-has-Agent)] [k=3]
  (B) Dist[row-has-Agent;up_row;row-has-Adversary] [k=4]
  (C) Dist[cell-has-Agent;adjacent_cell;cell-has-Adversary] [k=4]
\end{Verbatim}

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND C>0 AND B>0 -> {A INCs, B NILs, C NILs}, {A NILs, B DECs, C NILs}
\end{Verbatim}

>>>>

%\subsection{Space Invaders - v0}
%\subsubsection{Description}

%\subsubsection{Features}
%\begin{Verbatim}[fontsize=\footnotesize]
    %(A) Num[col-hv-Agent] [k=1]
    %(B) Dist[col-hv-white_king;right_col;col-hv-black_king] [k=4]
%\end{Verbatim}

%\subsubsection{Policy}
%\begin{Verbatim}[fontsize=\footnotesize]
%  1. B=0 AND A>0 -> {B INCs, A DECs}, {B NILs, A NILs}, {B INCs, A NILs}
%  2. B>0 AND A>0 -> {B DECs, A NILs}, {B NILs, A NILs}, {B INCs, A DECs}, {B NILs, A DECs}
%\end{Verbatim}

%\subsubsection{Example of Game}
%\begin{Verbatim}[fontsize=\footnotesize]

%\end{Verbatim}

\subsection{Chase - v0}
\subsubsection{Description}
In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $rightup$, $right$, $rightdown$, $down$, $leftdown$, $left$, $leftup\}$. The agent can move only diagonally and the adversary can move in perpendicular directions.

\subsubsection{Training instances:}
\begin{Verbatim}[fontsize=\footnotesize]
#A.....#
#......#
#......#
#.....T#
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
\end{Verbatim}

\subsubsection{Policy (without no fixed action space)}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A>0 AND B=0 AND D>0 AND C>0 -> {A ↓, B ↑, C ↓, D ↓}, {A ↓, B ·, C ↓, D ↓}
  2. A=0 AND B=0 AND D=0 AND C>0 -> {A ↑, B ↑, C ↓, D ↑}, {A ↑, B ·, C ↓, D ↑}
  3. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ↓, C ↓, D ↓}, {A ↑, B ↓, C ↓, D ↓}
  4. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ↑, C ↑, D ↓}, {A ↑, B ↑, C ↑, D ↓}
  5. A=0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ↓}, {A ↑, B ↑, C ↓, D ↓},
                                    {A ·, B ·, C ↓, D ↓}, {A ↑, B ·, C ↓, D ↓}

@@

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
1.
....... # ....... # ....... # ....T.. # ...T... # ...T... #
....... # ....... # ....T.. # ....... # ....... # ...A... #
....... # ....T.. # ....... # ....... # ....A.. # ....... #
....T.. # ....... # ....... # ...A... # ....... # ....... #
....... # ....... # ..A.... # ....... # ....... # ....... #
....... # .A..... # ....... # ....... # ....... # ....... #
A...... # ....... # ....... # ....... # ....... # ....... #

2.
T..... # T..... # ...... # ...... # T..... # T.A... # ..A... # ...... #
...... # ...... # T..... # T..A.. # ...A.. # ...... # T..... # TA.... #
...... # ....A. # ....A. # ...... # ...... # ...... # ...... # ...... #
.....A # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
\end{Verbatim}

\subsection{Chase - v1}
\subsubsection{Description}
In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$. The agent can move twice per turn and the adversary can move only once.

\subsubsection{Training instances}
\begin{Verbatim}[fontsize=\footnotesize]
#A.....#
#......#
#......#
#.....T#
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
  (B) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]
  (D) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
\end{Verbatim}

\subsubsection{Policy (without no fixed action space)}
\begin{Verbatim}[fontsize=\footnotesize]
  1. A=0 AND B=0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  2. A=0 AND B>0 AND D>0 AND C>0 -> {A ·, B ·, C ·, D ↓}
  3. A=0 AND B=0 AND D>0 AND C=0 -> {A ·, B ·, C ·, D ↓}, {A ↑, B ·, C ·, D ↓}
  4. B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  5. A=0 AND D>0 AND C>0 -> {A ↑, B ·, C ·, D ↓}
  6. A>0 AND B=0 AND D>0 AND C>0 -> {A ·, B ↑, C ↓, D ·}, {A ·, B ·, C ↓, D ·}
  7. A=0 AND B=0 AND D=0 AND C>0 -> {A ·, B ·, C ↓, D ·}, {A ·, B ↑, C ↓, D ·}

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  ...... # ...... # ...... # .T.... # .T.... # .T.... # T..... # T..... # T..... #
  .T.... # .T.... # .T.... # ...... # ....A. # ...A.. # ...A.. # ..A... # .A.... #
  ...... # .....A # ....A. # ....A. # ...... # ...... # ...... # ...... # ...... #
  .....A # ...... # ...... # ...... # ...... # ...... # ...... # ...... # ...... #
\end{Verbatim}

\subsection{Chase - v2}
\subsubsection{Description}
In this domain an agent has to chase an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$. The agent and the adversary can move only once per turn. In this version of the Chase the agent cannot always win, because if the adversary plays optimally, the agent will never catch it, but we can compute a policy using the Bad(state) feature. Of course now the policy will not be complete.

\subsubsection{Training instances:}
\begin{Verbatim}[fontsize=\footnotesize]
#A.....#
#......#
#......#
#.....T#
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[Forall(adjacent_col,col-hv-AGENT)] [k=3]
  (B) Bool[And(row-hv-AGENT,row-hv-TARGET)] [k=3]
  (C) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
  (D) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
  (E) Bool[And(row-hv-TARGET,Forall(adjacent_row,row-hv-AGENT))] [k=5]
  (F) Dist[col-hv-TARGET;adjacent_col;col-hv-AGENT] [k=4]
\end{Verbatim}

\subsubsection{Policy (without no fixed action space)}
\begin{Verbatim}[fontsize=\footnotesize]
  1. C=0 AND D>0 AND B=0 AND F>0 AND A>0 -> {A ↑, B ·, C ·, D ·, E ·, F ↓},
                                            {A ·, B ·, C ·, D ·, E ·, F ↓}
  2. C=0 AND D=0 AND B=0 AND E=0 AND F=0 AND A>0 -> {A ·, B ·, C ·, D ↑, E ↑, F ·}
  3. C=0 AND D=0 AND B>0 AND E=0 AND F>0 AND A>0 -> {A ↓, B ·, C ↑, D ·, E ·, F ↓}
  4. C=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ↓}
  5. C=0 AND D=0 AND B=0 AND E=0 AND A>0 -> {A ·, B ·, C ·, D ↑, E ·, F ·}
  6. C=0 AND D=0 AND E=0 AND F>0 AND A>0 -> {A ↑, B ·, C ·, D ·, E ·, F ↓},
                                            {A ·, B ·, C ↑, D ·, E ·, F ↓},
                                            {A ↓, B ·, C ·, D ·, E ·, F ↓},
                                            {A ↑, B ·, C ↑, D ·, E ·, F ↓}
  7. C=0 AND D>0 AND B=0 AND E>0 AND F>0 AND A>0 -> {A ↓, B ·, C ·, D ·, E ·, F ↓},
                                                    {A ·, B ·, C ·, D ·, E ·, F ↓}
  8. C>0 AND D=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ·}
  9. C=0 AND D=0 AND B=0 AND E=0 AND F>0 AND A>0 -> {A ·, B ·, C ·, D ·, E ·, F ↓}

\subsubsection{Example of Game}
\begin{Verbatim}[fontsize=\footnotesize]
  ....... # ....... # ....... # ....... # ....... # ....... # ....T.. #
  ....... # ....... # ....... # ....... # ....T.. # ....T.. # ....... #
  ....... # ....... # ....T.. # ....T.. # ....... # ....... # ....... #
  ....T.. # ....T.. # ....... # ....... # ....... # ...A... # ...A... #
  ....... # ....... # ....... # ...A... # ...A... # ....... # ....... #
  ....... # ...A... # ...A... # ....... # ....... # ....... # ....... #
  ...A... # ....... # ....... # ....... # ....... # ....... # ....... # ...

   ....T.. # .....T. # .....T. # ......T # ......T # ....... #
   ....... # ....... # ....... # ....... # ....... # ......T #
   ...A... # ...A... # ....A.. # ....A.. # .....A. # .....A. #
   ....... # ....... # ....... # ....... # ....... # ....... #
   ....... # ....... # ....... # ....... # ....... # ....... #
   ....... # ....... # ....... # ....... # ....... # ....... #
   ....... # ....... # ....... # ....... # ....... # ....... #
\end{Verbatim}

\subsection{Shoot - v0}
\subsubsection{Description}
In this domain an agent has to shoot an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$. This game would be the equivalent of a check with the rook. If the agent manages to get in the opponent's row or column, the agent wins. Either the agent or the adversary may take one of the available actions per turn.

\subsubsection{Training instances:}
\begin{Verbatim}[fontsize=\footnotesize]
#A.....#
#......#
#......#
#.....T#
\end{Verbatim}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[And(col-hv-AGENT,col-hv-TARGET)] [k=3]
  (B) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
  (C) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. B>0 AND A=0 AND C>0 -> {A ↑, B ↓, C ·}
  2. B=0 AND A=0 AND C>0 -> {A ·, B ·, C ↓}
\end{Verbatim}

\subsection{Shoot - v0: Policy with fixed action space}

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Bool[Exists(left_col,col-hv-AGENT)] [k=3]
  (B) Bool[And(col-hv-AGENT,col-hv-TARGET)] [k=3]
  (C) Bool[And(col-hv-TARGET,Forall(left_col,col-hv-AGENT))] [k=5]
  (D) Dist[row-hv-AGENT;adjacent_row;row-hv-TARGET] [k=4]

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. do((3,)): {D>0, D ·, A>0, A ·, C>0, C ·, B=0, B ·}
  2. do((2,)): {D>0, D ·, A>0, A ↓, C>0, C ↓, B=0, B ↑}
  3. do((2,)): {D>0, D ·, A>0, A ·, C>0, C ↓, B=0, B ↑}
  4. do((0,)): {D>0, D ↓, A=0, A ·, C>0, C ·, B=0, B ·}
  5. do((3,)): {D>0, D ·, A=0, A ↑, C=0, C ·, B=0, B ↑}
  6. do((1,)): {D>0, D ↓, A>0, A ·, C=0, C ·, B=0, B ·}
  7. do((3,)): {D>0, D ·, A>0, A ·, C ·, B=0, B ↑}
  8. do((3,)): {D>0, D ·, A=0, A ↑, C=0, C ·, B=0, B ·}
\end{Verbatim}

\subsection{Shoot - v1}
\subsubsection{Description}
In this domain an agent has to shoot an adversary, he has a set of fixed actions $A$, that is~\{$up$, $right$, $down$, $left\}$. This game would be the equivalent of a check with the rook. The player who manages to get in the opponent's row before wins, the other player loses. Either the agent or the adversary may take one of the available actions per turn. In this version of Shoot the agent cannot always win, because if the adversary plays optimally, but we can compute a policy using the Bad(state) feature. Of course now the policy will not be complete.

\subsubsection{Features}
\begin{Verbatim}[fontsize=\footnotesize]
  (A) Num[Forall(adjacent_col,col-hv-AGENT)] [k=3]
  (B) Bool[Exists(up_row,Exists(up_row,row-hv-AGENT))] [k=5]
  (C) Bool[And(col-hv-AGENT,Exists(adjacent_col,col-hv-TARGET))] [k=5]
  (D) Bool[And(row-hv-AGENT,Exists(adjacent_row,row-hv-TARGET))] [k=5]
  (E) Dist[row-hv-AGENT;up_row;row-hv-TARGET] [k=4]
  (F) Dist[col-hv-AGENT;right_col;col-hv-TARGET] [k=4]

\subsubsection{Policy}
\begin{Verbatim}[fontsize=\footnotesize]
  1. C=0 AND D=0 AND B>0 AND F>0 AND E>0 AND A>0 -> {A ↓, B ·, C ·, D ·, E ·, F ↓},
                                                    {A ·, B ·, C ·, D ·, E ↑, F ·},
                                                    {A ·, B ·, C ·, D ·, E ·, F ↑},
                                                    {A ↑, B ·, C ·, D ·, E ·, F ↓}
  2. C=0 AND D=0 AND B=0 AND F>0 AND E>0 AND A>0 -> {A ↓, B ·, C ·, D ·, E ·, F ·},
                                                    {A ·, B ·, C ·, D ·, E ↓, F ·},
                                                    {A ·, B ↑, C ·, D ·, E ↓, F ·}
  3. D>0 AND F>0 AND E>0 AND A>0 -> {A ·, B ·, C ·, D ↓, E ↓, F ·}
  4. C>0 AND B>0 AND F>0 AND E>0 AND A>0 -> {A ↑, B ·, C ↓, D ·, E ·, F ↓},
                                            {A ↓, B ·, C ↓, D ·, E ·, F ↓}
  5. C>0 AND D>0 AND B=0 AND F>0 AND E>0 AND A>0 -> {A ↓, B ·, C ↓, D ·, E ·, F ↓},
                                                    {A ↑, B ·, C ↓, D ·, E ·, F ↓}
  6. D>0 AND B=0 AND F>0 AND E>0 AND A>0 -> {A ·, B ↑, C ·, D ↓, E ↓, F ·}
  7. C>0 AND F>0 AND E>0 AND A>0 -> {A ↓, B ·, C ↓, D ·, E ·, F ↓},
                                    {A ↑, B ·, C ↓, D ·, E ·, F ↓},
                                    {A ·, B ·, C ↓, D ·, E ·, F ↓}
  8. D>0 AND B>0 AND F>0 AND E>0 AND A>0 -> {A ·, B ↓, C ·, D ↓, E ↓, F ·}
  9. C>0 AND D>0 AND F>0 AND E>0 AND A>0 -> {A ·, B ·, C ↓, D ·, E ·, F ↓}
  10. C>0 AND D=0 AND B>0 AND F>0 AND E>0 AND A>0 -> {A ·, B ·, C ↓, D ·, E ·, F ↓}
\end{Verbatim}
